---
title: "Access Gitea from R"
author: "ixpantia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Why gitea?
Gitea is a community managed, lightweight code hosting solution  were projects
and their respective git repositories can be managed  <https://gitea.io>. This
package gives an interface to the 'Gitea' API to  access and manage
repositories, issues and organizations directly in R.

## Get information about your projects

Some of the principal functions that you can use on the gitear package are
`create_issue()`, `get_issues_open_state()`, `get_issues_closed_state()`, among
others.

If you want to use this functions you can follow the nest step by step code:
```{r}
# Write your gitea credentials:
url <- "your gitea url" 
api <- "The api key"
project <- "The name of your project"
repository <- "Your repository name"
```


### create_issue()
With this function you can create an issue that it's going to appear on your
repository of interest
```{r}
issue_title <- "Execute exploratory data analysis on inicial set"
issue_body <- "Focus on: Data validation (Are data frame columns conforming to expected data types?), Data Integrity (Are all sources yielding expected row counts?), Signal strength (Flat variables (eg. extremely low variance))"

create_issue(base_url = url, api_key = api, owner = project, repo = repository,
             title = issue_title, body = issue_body)
```

### get_issues_open_state()
This function allows you to get the data of all the issues that have an open
state on your gitea environment.

```{r}
open_issues <- get_issues_open_state(base_url = url, api_key = api, 
                                     owner = project, repo = repository)
```



